%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Short Stylish Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Stefano (http://stefano.italians.nl/archives/63)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% The two fonts used in this template: Adobe Garamond Pro and Gill Sans
% do not come with Windows by default. You will need to download them in
% order to get an output as in the preview PDF. Otherwise, change those 
% fonts to fonts that do come with Windows or comment out the lines to use 
% the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{scrlttr2}

\usepackage{fontspec} % Allows font customization
\usepackage{marvosym} % Allows the use of symbols
\usepackage[english]{babel} % Required to compile in Windows

\setlength\parindent{0pt} % Removes all indentation from paragraphs

\defaultfontfeatures{Mapping=tex-text}
%\setmainfont {Adobe Garamond Pro} % Main document font
%\setsansfont {Gill Sans} % Used in the from address line above the to address

\renewcommand{\normalsize}{\fontsize{10.5}{15}\selectfont} % Sets the font size and leading

%----------------------------------------------------------------------------------------
%  PERSONAL INFORMATION
%----------------------------------------------------------------------------------------

\setkomavar{fromname}{Abhijit Chowdhary} % Your name
\setkomavar{fromaddress}{9331 Ridings Way\\Laurel\\MD} % Your address
\setkomavar{fromphone}{(240) 715-8308} % Your phone number
\setkomavar{fromemail}{abhijit9331@gmail.com} % Your email address
\setkomavar{place}{} % City written before the date, put your city here if you want this
\setkomavar{signature}{Abhijit Chowdhary} % Your name as you want it to appear in the signature

% These are not used in this document, uncomment if you would like to use them and refer to them as \usekomavar{name}
%\setkomavar{fromfax}{+1 (1)23 456789} % Your fax number
\setkomavar{fromurl}{https://abhijit-c.github.io/} % Your personal website
%\setkomavar{frombank}{Postbank 9307157}

%----------------------------------------------------------------------------------------
%  HEADER SECTION
%----------------------------------------------------------------------------------------

\firsthead{
\centering
{\addfontfeature{LetterSpace=15.0}\fontsize{24}{24}\selectfont\scshape \usekomavar{fromname}}\\[5mm]
\fontsize{18}{18}\selectfont\scshape Student at NYU } % Your current job title

%----------------------------------------------------------------------------------------
%  FOOTER SECTION
%----------------------------------------------------------------------------------------

\firstfoot{
\centering
\addfontfeature{LetterSpace=20.0}\scshape
{
\renewcommand{\\}{\ {\large\textperiodcentered}\ }
\usekomavar{fromaddress}
}\\
{\Large\Letter} \usekomavar{fromemail} \ {\Large\Telefon} \usekomavar{fromphone}
\ {\Large\Pickup} \usekomavar{fromurl} % If you want your fax number or website URL showing, add it here; you may need to play around with spacing
}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
% COVER LETTER CONTENTS
%----------------------------------------------------------------------------------------

\begin{letter}{ % Address of the company you are applying to
Auburn University\\
Parallel and Distributed Computing REU
%12345 City, State
}

%\setkomavar{subject}{Cover Letter} % This is the bold text saying 'Cover Letter', remove it if you don't like it
\opening{Dear Sir or Madam,}

I'm largely interested in Computational Mathematics, specifically in the pursuit
of optimizing the algorithms for these types of problems. Therefore, fields such
as Numerical Linear Algebra, Computational Number Theory, Cryptography,
and Numerical Optimization are very attractive to me. In addition, I have a
substatial interest in the methods to accomplish such tasks, such as compilers,
and methods of high performance computing, notably distributed and parallel
computation.

I realized this when recenetly I worked on a course project that could have
benefited from parallelization. In my graduate Geometric Modeling course, which
was a cross between computer graphics and discrete differential geometry, my
final project was to implement a paper \textit{Algebraic Point Set Surfaces} by
Gunnebaud and Gross. Roughly speaking, in graphics when we want to turn a point
cloud, read by some kind of scanner, into a triangularized mesh, we do an
optimization on algebraically fit planes to the point cloud, minimizing
distances. But, this paper proposed a fast method to fit spheres to the data
using an interesting "linear under certain circumstances" approximation, which
was advantageous in regions of high curvature. 

What really plagued me in this project wasn't the actual graphics theory .
Rather I spent days spinning my wheels in the implementation, trying to reduce
the bottleneck in the eigenvalue system construction and solve, trying various
different sparsity arguments and decompositions. Later I realized, that I could
have seriously improved performance using a library like OpenMP to parallize the
construction of the matrix and the actual solve. That's when I began to look
into parallel computation. 

Next semester, I'm taking a HPC course on this with the hopes of improving my
finite field polynomial library with it, and I hope to be able to apply my
new abilities in this REU with any professor looking into parallel numerical
methods or similar. I'm very interested in this field, as I consider the next
step in numerical methods.

Sincerely yours, \usekomavar{signature}.

%----------------------------------------------------------------------------------------

\end{letter}
\end{document}
